\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage[top=0.65in, bottom=0.65in, left=0.65in, right=0.65in]{geometry} 
\usepackage{multicol}
\setlength{\hintscolumnwidth}{0.13\textwidth}


% Personal info
\name{Xicheng}{Xie}
\phone[mobile]{+1~(336)~448~8191}
\email{xicheng.xie@northwestern.edu}
\social[linkedin]{xx0224}
\social[github]{xx2416}
\address{}{Chicago, IL}{USA}



\begin{document}

\makecvtitle

% Education
\section{Education}
\cventry{09/2024 -- Present}{Ph.D. in Biostatistics}{Northwestern University, Feinberg School of Medicine}{Chicago, IL}{}{}
\cventry{09/2022 -- 05/2024}{M.S. in Biostatistics}{Columbia University, Mailman School of Public Health}{New York, NY}{}{}
\cventry{09/2018 -- 06/2022}
{B.S. in Environmental Science}
{Shanghai Jiao Tong University \textit{(Top \textbf{4} university in China)}}
{Shanghai, China}{}{}

% Skills
\section{Technical Skills}
\cvitem{Programming}{Python (PyTorch, TensorFlow, Keras, Scikit-learn, NumPy, Pandas, Matplotlib, Seaborn), 
R (glmnet, caret, dplyr, MASS, Shiny, Bioconductor, ggplot2), SQL, MATLAB, SAS, Shell/SSH}

\vspace{6pt}
\cvitem{Methodologies}{
Machine Learning (supervised, unsupervised, reinforcement learning), Deep Learning (CNN, RNN, LSTM, Transformers), Bayesian Statistics, 
Statistical Inference, Causal Inference, Time-Series Forecasting, Survival Analysis, Longitudinal Data Analysis, Missing Data Imputation, Optimization, A/B Testing
}
\vspace{6pt}
\cvitem{Tools \& Platforms}{
MySQL, PostgreSQL, PyCharm, Jupyter Notebook/Lab, RStudio, AWS, Microsoft Azure, Git/GitHub, Slurm/HPC, Docker, Linux/Unix
}


% Experience
\section{Experiences}

\cventry{02/2024 -- 09/2024}{Data Scientist}{IQVIA}{Shanghai, China}{}{
\begin{itemize}
    \item Built pipelines to extract influenza data from China CDC reports and Baidu Index data, creating a cleaned weekly time-series dataset (2012–2024).
    \item Engineered time-series features (lags, windows), performed dimensionality reduction, and applied model-based feature selection.
    \item Trained SARIMAX, LSTM, LightGBM, and XGBoost to predict ILI rates; SARIMAX improved short-term RMSE by 17\% and accuracy by 23\%.
\end{itemize}
}
\vspace{12pt}
\cventry{03/2023 -- 01/2024}{Data Analyst}{Columbia University}{New York, NY}{}{
\begin{itemize}
    \item Processed 40 years of US temperature data (12.7 GB) into a 500 MB longitudinal database on extreme heat events using Python and HPC.
    \item Developed Bayesian models to evaluate and forecast heat stress variations at the census-tract level nationwide, identifying vulnerable areas and groups.
    \item Built 2 interactive RShiny apps visualizing extreme heat and hurricane mortality, increasing climate report engagement of Grist by 12\%.
\end{itemize}
}
\vspace{12pt}
\cventry{01/2022 -- 09/2022}{Applied ML Engineer Intern}{Fresenius Medical Care}{Shanghai, China}{}{
\begin{itemize}
    \item Analyzed clinical and hemodynamic data from 600+ dialysis patients using Azure and Python to identify patient patterns.
    \item Built preprocessing and feature engineering pipelines to improve data quality for model training.
    \item Trained semi-supervised models (Random Forest, S3VM) to classify AV fistula conditions with 89.72\% accuracy, enhancing patient stratification and informing treatment protocols.
\end{itemize}
}

\newpage
% Projects
\section{Projects}

\cvitem{Retail Pharmacy Forecasting}{
\begin{itemize}
    \item Forecasted SKU-level daily sales across 11 retail pharmacies using LSTM (TensorFlow) and Bayesian models (PyMC3) on 6 years of data.
    \item Engineered time-series features from 1,095-day sequences per SKU; improved prediction accuracy by 13.7\% over baseline.
    \item Applied Fuzzy C-Means clustering to segment SKUs by sales patterns and seasonality, increasing inventory turnover by 12\%.
\end{itemize}}

\cvitem{NYC Restaurant Recommendations}{
\begin{itemize}
    \item Extracted and integrated real-time data from 8,000+ NYC restaurants (Yelp API, CSS scraping) with DOHMH inspection records; curated 6,943 clean entries.
    \item Built a hybrid recommendation engine using content-based filtering and clustering (K-Means + cosine similarity) based on cuisine, price, inspection grade, and location.
    \item Deployed an interactive R Shiny app with GeoSearch API for personalized, location-aware recommendations and inspection-aware filtering.
\end{itemize}}

\cvitem{Multi-Omics Cancer Subtyping}{
\begin{itemize}
    \item Developed a perturbation-based spectral clustering algorithm in R for subtyping TCGA patients using mRNA, miRNA, and DNA methylation data.
    \item Identified biologically distinct subtypes for KIRC, GBM, and LAML with Cox survival p-values $<$ 0.01; validated clustering with RI = 0.91 and ARI = 0.78 across 8 benchmark datasets.
\end{itemize}}


% Publications
\section{Publications}

\noindent Lynch, V.D., Sullivan, J.A., Flores, A.B., \textbf{Xie, X.}, Aggarwal, S., Nethery, R.C., Kioumourtzoglou, M.-A., Nigra, A.E., Parks, R.M. (2025). \textit{Large floods drive changes in cause-specific mortality in the United States}. \textit{Nature Medicine}, \textbf{31}, 663–671. \href{https://doi.org/10.1038/s41591-024-03358-z}{https://doi.org/10.1038/s41591-024-03358-z}

\medskip

\noindent Meltzer, G.Y., Anderson, G.B., \textbf{Xie, X.}, Casey, J.A., Schwartz, J., Bell, M.L., Van Horne, Y.O., Fox, J., Kioumourtzoglou, M.-A., Parks, R.M. (2025). \textit{Disruption to test scores after hurricanes in the United States}. \textit{Environmental Research: Health}, \textbf{3}(2), 025003. \href{https://doi.org/10.1088/2752-5309/adb32b}{https://doi.org/10.1088/2752-5309/adb32b}

\medskip

\noindent \textbf{Xie, X.C.}, Huang, W.W., Shen, G.Q., Yu, H., Wang, L.M. (2022). \textit{Selection and colorimetric application of ssDNA aptamers against metamitron based on magnetic bead-SELEX}. \textit{Analytical Methods}, \textbf{14}(31), 3021–3032. \href{https://doi.org/10.1039/d2ay00566b}{https://doi.org/10.1039/d2ay00566b}

\medskip

\noindent Yu, H., Pan, C.Q., Zhu, J.X., Shen, G.Q., Deng, Y., \textbf{Xie, X.C.}, Geng, X.Q., Wang, L.M. (2022). \textit{Selection and identification of a DNA aptamer for fluorescent detection of netilmicin}. \textit{Talanta}, \textbf{250}, 123708. \href{https://doi.org/10.1016/j.talanta.2022.123708}{https://doi.org/10.1016/j.talanta.2022.123708}
\medskip

\noindent Shi, Y.Z., \textbf{Xie, X.C.}, Wang, L.M., Wang, L.Z., Li, L.Y., Yan, Z.Y., Shen, G.Q. (2022). \textit{Fluorescent assay for carbendazim determination using aptamer and SYBR Green I}. \textit{Australian Journal of Chemistry}, \textbf{75}(5), 345–352. \href{https://doi.org/10.1071/ch22001}{https://doi.org/10.1071/ch22001}
\medskip

\noindent \textbf{Xie, X.C.}, Li, L.Y., Wang, L.M., Pan, C.Q., Zhang, D.W., Shen, G.Q. (2021). \textit{Colourimetric detection of tebuconazole in aqueous solution based on an unmodified aptamer and the aggregation of gold nanoparticles}. \textit{Australian Journal of Chemistry}, \textbf{74}(12), 838–846. \href{https://doi.org/10.1071/ch21171}{https://doi.org/10.1071/ch21171}

\end{document}
